OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2022-01-13 paper/paper.Rmd
Fix behavior of PDFs without figures

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(fig.path = dplyr::if_else(params$include_figures, 
                                                'figures/',
                                                'blanks/'),
                      dpi = 300
                      )
```

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(fig.path = dplyr::if_else(params$include_figures, 
                                                'figures/',
                                                'figures/blanks/'),
                      dpi = 300
                      )
```

### 2022-01-13 paper/paper_before-review.Rmd
Fix behavior of PDFs without figures

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(fig.path = 'figures/',
                      dpi = 300)
```

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(fig.path = dplyr::if_else(params$include_figures, 
                                                'figures/',
                                                'figures/blanks/'),
                      dpi = 300)
```
